Minimizing post-shock forecasting error using disparate information

### 2020-07-09 manuscript/manuscript.tex
updated manuscript; comments are provided; next steps are provided

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=1in}

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} % IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E#1{\mathrm{E}(#1)} % Expectation symbol
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}

@@

Things to do:
\begin{enumerate}
  \item Need to add simulations. 
  \item $\mu_{\alpha}=2$, $X_{i,t}\sim \Gamma(1,2)$, $\delta_i, \gamma_i \sim \normal{1}{0.5}$
  \item $\sigma=10$ for the base case.
  \item $\sigma_{\alpha}= (5, 10, 25, 50, 100)$
  \item $\sigma= (5, 10, 25, 50, 100)$
\end{enumerate}

@@

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
\end{enumerate}

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.  However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error. Then, we discuss some frequently used methodologies that may be applied in this situation.
%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.

@@

As alternatives to forecast combination, data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas. Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  Recent researches in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction, whose ideas are similar to ours. For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
  \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock. To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures. Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a ``shock'' at time point $T_1^*+1 = 126$. It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 

@@

    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .

@@

where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 

@@

$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that

@@

     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}

@@

     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}

@@

    \end{pmatrix}.

@@

Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $2p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique. If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).  The issue of non-uniqueness is further discussed in Section \ref{discussion}.

@@

As Section \ref{conditions} and \ref{comparisons} detailed the conditions for risk-reduction and comparisons, they usually involve fixed quantities related to variance and expectation. To make use of those properties in practice, estimation is required. Section \ref{varbootstrap} will introduce a general procedure of parametric bootstrap under the context of the problem to attain this purpose.

\subsection{Conditions for risk-reduction for shock-effects estimators}
\label{conditions}

@@

In terms of the adjustment estimator, $\hat{\alpha}_{\rm adj}$, (\ref{riskconditionadj}) implies two facts: (1) Forecast 2 is preferable to Forecast 1 asymptotically in $n$ 
whenever $\mu_{\alpha} \neq 0$; (2) In finite pool of time series, Forecast 2 is preferable to 
Forecast 1 when the $\mu_{\alpha}$ is large relative to its variability and 
overall regression variability.   %This result is also intuitive. For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.  See Section \ref{forecast} for forecast formulation for details.

For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and variance expression of $\hat{\alpha}_{\rm wadj}$, the following is the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$.
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
\end{align*}
In this case, Forecast 2 is preferable to Forecast 1 when $\mu_{\alpha}$ is large relative to the \emph{weighted sum of variances for shock effects for other time series} and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$. Section  \ref{varbootstrap} will provide a detailed treatment about how to deal with these technical inequalities in practice.

\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{conditionsm2122}
The $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. %It is a more reasonable and general model since it is often the case that shock-effects differ by means among disparate time series in practice. $\mc{M}_{22}$  further adds the random effect structure of $\delta$ and $\gamma$ to  $\mc{M}_{21}$ for generalization.
However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$. %From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}. 
We now state conditions for risk reduction.

@@

Based on Proposition \ref{propriskwadj2}, we can obtain a similar inequality as in Section \ref{conditionsmodel1} as below
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i} < (\E{\alpha_1})^2,
\end{align*}
where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}.

Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally. Hence, Proposition \ref{proprisk} no longer  holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$. But, as an alternative, we can derive similar conditions as below. By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
\begin{align*}
 \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
 &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\end{align*}
Therefore, the above inequality will simply to 
\begin{align*}
 (\E{\alpha_1})^2
 &>\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{align*}
Note that since $\hat{\alpha}_{\rm adj}$ is biased for $\E{\alpha_1}$, the bias term $(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2$ will become complicated and  simplification yields no insightful results.

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. In other words, $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.

Topics of  evaluation of these inequalities in practice can be found in Section \ref{varbootstrap}. 
We will discuss comparisons of adjustment estimators in the the next Section.
%As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.

@@

Denote the risk-reduction quantity for the adjustment estimator as $\Delta_{\rm adj}$, the one for inverse-weighted estimator as $\Delta_{\rm IVW}$, and the one for weighted-adjustment estimator as $\Delta_{\rm wadj}$. As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration. For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.

According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
\begin{align*}
  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
\end{align*}
From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.

@@

\subsubsection{Proofs for lemmas and propositions}

>>>>

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=0.8in}

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E#1{\mathrm{E}(#1)} % Expectation symbol
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}

@@

@@

\begin{enumerate}
  \item Revisions to the manuscript.
  \item Detailed comments for further revisions are included.
  \item The Supplementary Materials document has been expanded. More comments are included in that document.
  \item The fixed donor pool bootstrap procedure (previously called $B_c$) is moved to the Supplementary Materials document.
  \item Commentary about bootstrap consistency is removed, I do not think that it is necessary.
  \item The ``best estimator'' materials are removed, this procedure did not perform too well.
\end{enumerate}

\noindent{\bf Things to do}: We also need a simulation corresponding to model $\mc{M}_1$ in which we investigate the performance of all adjustment estimators. We should also do a very small simulation that checks whether or not the weighted adjustment estimator does well when we expect $\mathbf{W}^*$ to be on the boundary.

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.  However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error. %Then, we discuss some frequently used methodologies that may be applied in this situation.
%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.

@@

Data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas. Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  Recent developments in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction. %whose ideas are similar to ours. 
For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
  \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock (\textbf{What does Up to the scale of the shock mean? Why will the model-free technique not work ideally?}). To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed. Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the performance of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively. Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a shock on March 9th, 2020. The proposed three aggregation techniques work much better than no adjustment in this example. We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts. We now motivate our aggregation techniques.

@@

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a shock at time point $T_1^*+1 = 126$. It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock prediction methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 

@@

    \mbf{x}_{1, T_1^*}' \\ \mbf{x}_{1, T_1^*+1}'
  \end{pmatrix},
  \quad  
  \mbf{X} = \begin{pmatrix}
  	\mbf{x}_{2, T_2^*}' \\
    \mbf{x}_{2, T_2^*+1}' \\
    \vdots \\
  	\mbf{x}_{1, T_{n+1}^*}' \\
    \mbf{x}_{2, T_{n+1}^*+1}'
  \end{pmatrix},
  \quad \text{and} \quad 
  \hat{\mbf{X}}_1(\mbf{W}) 
    = (\mbf{W}' \otimes \mbf{I}_2) \mbf{X}

@@

where $\otimes$ is the kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 

@@

$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that

@@

     \mbf{x}_{2, T_2^*}' \\
      \mbf{x}_{2, T_2^*+1}'

@@

     \mbf{x}_{n+1, T_{n+1}^*}' \\
      \mbf{x}_{n+1, T_{n+1}^*+1}'

@@

    \end{pmatrix}'.

@@

Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $2p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique. If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).  The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.

@@

Sections \ref{conditions} and \ref{comparisons} detail conditions needed for risk-reduction and comparisons of adjustment estimators. These conditions involve variances and expectations which may be difficult to compute in practice. To make use of those properties in practice, estimation is required. Sections \ref{varbootstrap} and \ref{loocv} introduce  parametric bootstrap and leave-one-out cross validation procedures which prospectively estimate the conditions necessary for risk-reduction without observation of the post-shock response for the time series under study. Our simulations test these procedures.

\subsection{Risk-reduction conditions for shock-effects estimators}
\label{conditions}

@@

Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.   %This result is also intuitive. For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.  See Section \ref{forecast} for forecast formulation for details.

For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
\end{align*}
In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$. Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to deal with these technical inequalities in practice.

\subsubsection{Conditions under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{conditionsm2122}

The shock-effects $\alpha_i$s have different means under $\mc{M}_{21}$ and $\mc{M}_{22}$ unlike under $\mc{M}_1$. %It is a more reasonable and general model since it is often the case that shock-effects differ by means among disparate time series in practice. $\mc{M}_{22}$  further adds the random effect structure of $\delta$ and $\gamma$ to  $\mc{M}_{21}$ for generalization.
However, Proposition \ref{unbiased} implies that $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$. %From Proposition \ref{varprop}, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$  will be as in Proposition \ref{propriskwadj2}. 
We now state conditions for risk-reduction.

@@

Based on Proposition \ref{propriskwadj2}, we can obtain a similar inequality as in Section \ref{conditionsmodel1} as below
\begin{align*}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 \var{\alpha_i} < (\E{\alpha_1})^2,
\end{align*}
where $\var{\alpha_i}$ may be replaced with $\sigma^2_{\alpha}$ in $\mc{M}_{21}$. The conclusions and intuitions will be identically the same as what we have in Section \ref{conditionsmodel1}. Proposition \ref{unbiased} shows that $\hat{\alpha}_{\rm adj}$ is a biased estimator of $\E{\alpha_1}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$ generally. Hence, Proposition \ref{proprisk} no longer holds for $\hat{\alpha}_{\rm adj}$ under $\mc{M}_{21}$ and $\mc{M}_{22}$.

As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting. By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
\begin{align*}
 \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
 &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{align*}
The above inequality simplifies to 
\begin{equation} \label{ineq}
 (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{equation}
Note that since $\hat{\alpha}_{\rm adj}$ is biased for $\E{\alpha_1}$, the bias term $(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2$ will become complicated and simplification yields no insightful results. We can however estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. In other words, $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$. Evaluation of these inequalities in practice can be found in Sections \ref{varbootstrap} and \ref{loocv}. We will discuss comparisons of adjustment estimators in the the next section.
%As conditions of risk-reduction for individual estimators are obtained, a natural question arises --- which one is better? It will be discussed in Section \ref{comparisons}.

@@

Denote the risk-reduction quantities for adjustment estimators as $\Delta_{\rm adj}$, $\Delta_{\rm IVW}$, and $\Delta_{\rm wadj}$, respectively for standard adjustment, inverse-variance weighted estimator, and weighted-adjustment estimato. %As long as the risk-reduction of one estimator is greater than those of others, we will vote it as the best estimator among our pool of estimators for consideration. For example, if we find that $\Delta_{\rm wadj}>\Delta_{\rm adj}$ and $\Delta_{\rm wadj}>\Delta_{\rm IVW}$, the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$ is the most favorable.
According to  discussion in Section \ref{conditionsm2122}, we know that under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, the risk-reduction quantity for $\hat{\alpha}_{\rm IVW}$ is
\begin{align*}
  \Delta_{\rm IVW} = (\E{\alpha_1})^2- \var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2.
\end{align*}
From discussions in Section \ref{conditions}, we know that the risk-reduction quantities for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ differ across models, we will discuss in different cases accordingly.

@@

\subsection{Proofs for lemmas and propositions}
